The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-12 main.tex
added footnote about widespread use of ci-helpers

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to enable package maintainers to control their testing setup
and installation process for various CI services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI\footnote{\url{https://travis-ci.org/}} and
Appveyor CI\footnote{\url{https://www.appveyor.com/}}.

>>>>

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to enable package maintainers to control their testing setup
and installation process for various CI services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread\footnote{Approximately 30\%
of the ci-helpers contributor are coming from outside the astropy community and 
there are currently 292 repositories on github that has ci-helpers in their travis configuration file.}. The current
tools support configuration for Travis CI\footnote{\url{https://travis-ci.org/}} and
Appveyor CI\footnote{\url{https://www.appveyor.com/}}.
